Model

### 2019-08-28 stats/model.Rmd
new model with subject intercepts

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
      }

@@

# load this for model parameters with so_slope (0:2)
#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

@@

```{r work in progress}
semStr <- '
var data = dataFromR.data

@@

@@

  // global parameters
  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})

  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})

  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})

  var participant_age_adjust = gaussianDrift({mu: 0, sigma: 1, width: 0.2})

  var sem_slope_item = repeat(familiars.length, function(){
    gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5} )
  })

  var sem_int_item = gaussianDrift({mu: sem_int_global, 
        sigma: item_int_sigma, width: 0.5})

      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)

      var speakerOptimality = so_int  + so_slope * age

@@

      query.add(["modelPrediction", cndtn], [age, Math.exp(modelPredictions.score(1))])

    query.add(["parameter", cndtn], [sem_int_item, sem_slope_item])

  query.add(["parameter", "speaker_optimality"], [so_int, so_slope])
  query.add(["parameter", "global_sem"], [sem_int_global, sem_slope_global])
  query.add(["parameter", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])

@@

>>>>

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: Math.pow(gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        }), 2)
      }

@@

# load this for model parameters with so_slope (0:2)
sem_know_model <- readRDS("../saves/sem_know_new_model.rds")

@@

subj | item | response
1    |  A  |   1
1    |  B  |   1
2    |  A  |   1
2    |  B  |   0

```{js}

var sampleItemParameters = function() { 
  return {
      intercept: gaussianDrift({
        mu: globalLineParameters.intercept, 
        sigma: itemVariability.intercept, 
        width: 0.5
      }),
      slope: Math.pow(gaussianDrift({
        mu: globalLineParameters.slope, 
        sigma: itemVariability.slope, 
        width: 0.5
      }), 2)
    }   
}

// want something that favors smaller values
var subject_sigma = uniform(0, 1)

var sampleLinguisticCompetence = function(age){
  return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.5 })
}

// [ carrot, duck, bread, ...]  (slope and intercept)
var all_item_parameters = repeat(n_items, sampleItemParameters)
// [s1, s2, s3, ...] (intercept)
var all_subject_parameters = map(sampleLinguisticCompetence, subjects)

var sem_knowledge = logistic(item.intercept +  item.slope * linguistic_competence)
```

```{r work in progress}
sem_subj_str <- '
var data = dataFromR.data

@@

var familiars = levels(data, "familiar")
var subjects = levels(data, "subid")

@@

  var sampleItemParameters = function(itemName) { 
    return [itemName, {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: Math.pow(gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        }), 2)
      }]
  }

  // {papaya: {int, slope}, bread: {int, slope}, ... }
  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))

  // want something that favors smaller values
  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})

  var sampleLinguisticCompetence = function(age){
    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
  }

  foreach(function(subid){
      var subjectData = _.filter(data, {subid: subid})
      var subj_age = subjectData[0].age
      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)

      // question: should we use age here instead of the random intercept? or a different random intercept?
      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_linguistic_competence

      // each row is a different item
      foreach(function(row){

        var itemLineParameters = all_item_parameters[row.familiar]

        var sem_knowledge = logistic(itemLineParameters.intercept + 
            itemLineParameters.slope * subj_linguistic_competence)

@@

        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])

      }, subjectData)

    // comment out to save memory
    query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])

  }, subjects)

  foreach(function(item){
    var itemLineParameters = all_item_parameters[item]
    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
  }, familiars)

  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH",
                        samples = 5,
                        burn = 1,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1)
)
